\documentclass[14pt]{extarticle} % extarticle allows larger font options than 12pt
\usepackage{enumitem} % for easier alphabetic labels in enumerate.
\usepackage{nopageno} % no page numbers
\usepackage[margin=1.0in]{geometry}

\begin{document}
\hfill Tristan\\
\null\hfill 28 September 2022

\vspace{10mm}

\begin{enumerate}[label=\Alph*.), itemsep=\fill]
    \item  Doug Upp must shovel a pile containing $50ft^3$ of sand into a dump truck. With each scoop he decreases the size of the pile by $\frac{1}{6}ft^3$. Let $x$ be the number of scoops he has shoveled.
    \begin{enumerate}[itemsep=\fill]
        \item Write an expression for the number of cubic feet of sand left after $x$ scoops.
        \item How much sand is left after 12 scoops?
        \item How much sand is left after 100 scoops?
        \item Doug takes a rest when $20 ft^3$ of sand remains. Write an equation stating that $20 ft^3$ of sand remain. Then solve the equation for the number of scoops Doug took before the rest.
    \end{enumerate}
\vfill\clearpage
    \item  When the meter in a taxi is first turned on, it reads \$1.20. As the taxi travels, \$1.60 is added for each mile driven. 
    \begin{enumerate}[itemsep=\fill]
        \item Write an expression for the number of dollars the meter reads after $x$ miles.
        \item How much would you pay to ride 5 miles?
        \item How much would you pay to ride 13 miles?
        \item Write an equation stating that you paid \$12.40. Then solve the equation to find out how far you rode.
        \item How far could you ride for \$33.20?
    \end{enumerate}
\vfill\end{enumerate}
\end{document}